True versus apparent shapes of bow shocks

### 2017-11-20 papers/Paper1/quadrics-bowshock.tex
Add plan of paper to intro of theory paper
Convert first part of quadrics section to planitude-alatude notation
Port the conic figures to the new notation
Move the ancantoid derivation to an appendix
Finish Appendix B on ancantoids!
Re-write derivation of planitude for ancantoids
Note that C_{k\beta} is now 2 x what it was before
Re-write derivation of alatude for ancantoids
Re-do the ancantoid shape graphs
Finish reorganization/expansion of Appendix C
Finish sec 5.2 on true shapes of cantoids and ancantoids
Re-do the projected ancantoid fig and start describing it
Re-organize the dust wave se

\title[Bow shock shapes]{True versus apparent shapes of bow shocks and bow waves}

@@

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Astrophysical bow shocks are a common result of the interaction
  between supersonic plasma flows, such as winds or jets from stars or
  active galaxies.  Similarly shaped radiation bow waves are produced
  by the relative motion between dust grains and a luminous source.
  For cylindrically symmetric bow shocks and waves, we develop a
  general theory for the effects of inclination angle on the apparent
  shape. We propose a new two-dimensional classification scheme for
  bow shapes, which is based on dimensionless geometric ratios that
  can be estimated from observational images.  The two ratios are
  related to the flatness of the bow's apex, which we term
  \textit{planitude} and the openness of its wings, which we term
  \textit{alatude}.  We calculate the expected distribution on the
  planitude--alatude diagram for a variety of simple geometrical and
  physical models: quadrics of revolution, wilkinoids, cantoids,
  ancantoids, and dragoids.  We further show how these are modified in
  the presence of small-amplitude standing-wave oscillations of the
  basic shape, as may be produced by hydrodynamic instabilities or a
  time-varying source.
\end{abstract}

@@

\input{sec-intro}
\input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
\clearpage
\input{app-dust-wave}
\clearpage
\input{sec-standing-wave}
\input{sec-conclusions}
\clearpage
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-parabola}
\input{app-rcurv}
\input{app-r90}
\input{app-wilkinoid}

>>>>

\title[Bow shock shapes]{True versus apparent shapes of bow shocks}

@@

\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\Sin}{\mathcal{S}}
\DeclareMathOperator{\Cos}{\mathcal{C}}
\DeclareMathOperator{\Cot}{\mathcal{T}}
\DeclareMathOperator{\GammaFunc}{\Gamma}
\newcommand\w{\ensuremath{\mathrm{w}}}
\newcommand\C{\ensuremath{\mathrm{c}}}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\Abs}[1]{\left\lvert#1\right\rvert}
\newcommand\TODO[1]{%
  \begin{center}
    \framebox{\parbox{0.8\linewidth}{
        \texttt{\footnotesize\color{red} #1}}}
  \end{center}}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
\begin{abstract}
  Astrophysical bow shocks are a common result of the interaction
  between supersonic plasma flows, such as winds or jets from stars or
  active galaxies.  Similarly shaped radiation bow waves are produced
  by the relative motion between dust grains and a luminous source.
  For cylindrically symmetric bow shocks and waves, we develop a
  general theory for the effects of inclination angle on the apparent
  shape. We propose a new two-dimensional classification scheme for
  bow shapes, which is based on dimensionless geometric ratios that
  can be estimated from observational images.  The two ratios are
  related to the flatness of the bow's apex, which we term
  \textit{planitude} and the openness of its wings, which we term
  \textit{alatude}.  We calculate the expected distribution on the
  planitude--alatude diagram for a variety of simple geometrical and
  physical models: quadrics of revolution, wilkinoids, cantoids,
  and ancantoids.  
\end{abstract}

@@

\input{sec-intro}
% \input{sec-generic-model}
\input{sec-projection}
\input{sec-conic}
\input{sec-thin-shell}
% \input{app-dust-wave}
% \input{sec-standing-wave}
\input{sec-conclusions}
\clearpage
\bibliographystyle{mnras}
%% All references should be put in the BibTeX file bowshocks-biblio.bib
\bibliography{bowshocks-biblio}
\appendix
\input{app-parabola}
\input{app-ancantoid}
\input{app-shape-parameters}
% \input{app-dust-equations}

### 2017-11-20 papers/Paper1/sec-conclusions.tex
Write first half of conclusions for Paper I

%\newcommand\thC{\(\theta^1\)\,Ori~C}
\defcitealias{Canto:1996}{CRW}

>>>>

We have shown that the shapes of stellar bow shocks can be usefully
characterized by two dimensionless numbers: the \textit{planitude},
\(\Pi\), or flatness of the bow's apex, and the \textit{alatude},
\(\Lambda\), or openness of the bow's wings.  The planitude and alatude can
be estimated from ratios of lengths that can be straightforwardly
measured from observations or theoretical models.  We develop a
general theory for the projected shape, \((\Pi', \Lambda')\), of a bow shock's
limb-brightened edge, or \textit{tangent line}, as a function of
inclination angle, \(i\), where the emission shell is idealized as a
cylindrically symmetric surface.

We first apply this theory to find inclination-dependent tracks on the
projected planitude--alatude plane for the special case of
\textit{quadric} surfaces, such as hyperboloids, paraboloids, and
spheroids, where the tangent line is a conic section.  The spheroids
and hyperboloids occupy distinct regions of the plane, with the
paraboloids defining the boundary between the two.  As the inclination
is increased from \(\abs{i} = 0\) (side-on) to \(\abs{i} = 90^\circ\)
(end-on), the tracks first tend to approach the diagonal
\(\Lambda' = \Pi'\), corresponding to confocal conics, always remaining within
their own region.  At the highest inclinations, the spheroids all
converge at \(\abs{i} = 90^\circ\) on the point
\((\Pi', \Lambda') = (1, 1)\) and the paraboloids on the point
\((\Pi', \Lambda') = (2, 2)\).  The hyperboloids, on the other hand diverge as
\((\Pi', \Lambda') \to (\infty, \infty)\) for a finite
\(i_{\mathrm{crit}}\), which depends on the hyperbolic eccentricity.
For \(\abs{i} > i_{\mathrm{crit}}\), the tangent line no longer exists
for the hyperbola, and it no longer would appear to be a bow shock.

We have presented a new two-dimensional classification scheme for the
analysis of the shapes of stellar bow shocks, which

### 2017-11-20 papers/Paper1/sec-dust-bow-intro.tex
Write first half of conclusions for Paper I

>>>>

The paper is organized as follows.
%
In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
dusty radiation bow wave (dragoids), including the effects of
gas-grain drag.
%
In \S~\ref{sec:perturbed-bows} we investigate the effects on the
planitude--alatude plane of small-amplitude perturbations to the bow
shape.
%

### 2017-11-20 papers/Paper1/sec-intro.tex
Re-organize the dust wave section a bit
Write first half of conclusions for Paper I

Bow shocks from pulsars and neutron stars
\citep{Cordes:1993a, Brownsberger:2014a}.

Radiation bow waves \citep{van-Marle:2011a}

The paper is organized as follows.
%
In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
are necessary for describing bow shapes and introduce two
dimensionless ratios: planitude and alatude.
%
In \S~\ref{sec:projection} we derive general results for the
projection of bow shapes on to the plane of the sky.
%
In \S~\ref{sec:conic} we apply the results to the simplest possible
class of geometric bow models: the quadrics of revolution, which
comprise spheroids, paraboloids, and hyperboloids, each of which
occupies a disjoint region of the planitude--alatude plane.
%
In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
models for the parallel-stream case (wilkinoids) and wind-wind case
(cantoids), including extension to an anisotropic inner wind
(ancantoids).  We calculate the location of the models in the
planitude--alatude plane as a function of the inclination of the bow
shock axis to the plane of the sky.
%
In \S~\ref{sec:shape-dust-wave} we do the same for simple models of a
dusty radiation bow wave (dragoids), including the effects of
gas-grain drag.
%
In \S~\ref{sec:perturbed-bows} we investigate the effects on the
planitude--alatude plane of small-amplitude perturbations to the bow
shape.
%
In \S~\ref{sec:conc} we summarise our results and outline how
following papers will apply these ideas to observations and numerical
simulations.

>>>>

\TODO{Bow shocks from pulsars and neutron stars
  \citep{Cordes:1993a, Brownsberger:2014a}.}

\TODO{Radiation bow waves \citep{van-Marle:2011a}.}

The paper is organized as follows.
%
In \S~\ref{sec:plan-alat-bow} we outline the geometric parameters that
are necessary for describing bow shapes and introduce two
dimensionless ratios: planitude and alatude.
%
In \S~\ref{sec:projection} we derive general results for the
projection of bow shapes on to the plane of the sky.
%
In \S~\ref{sec:conic} we apply the results to the simplest possible
class of geometric bow models: the quadrics of revolution, which
comprise spheroids, paraboloids, and hyperboloids, each of which
occupies a disjoint region of the planitude--alatude plane.
%
In \S~\ref{sec:crw-scenario} we consider thin-shell hydrodynamic
models for the parallel-stream case (wilkinoids) and wind-wind case
(cantoids), including extension to an anisotropic inner wind
(ancantoids).  We calculate the location of the models in the
planitude--alatude plane as a function of the inclination of the bow
shock axis to the plane of the sky.
In \S~\ref{sec:conc} we summarise our results and outline how
following papers will apply these ideas to observations and numerical
simulations.
